A meta analysis of tournaments and an evaluation of performance in the Iterated Prisoner's Dilemma.

### 2020-02-04 paper/main.tex
add sentence about new columns of perfomance

The top 15 strategies for each tournament type based on \(\bar{r}\) are given in
Table~\ref{table:top_performances}.

\newcolumntype{g}{>{\columncolor{Gray}}l}
\begin{table}[!htbp]
    \begin{center}
    \resizebox{.9\textwidth}{!}{
        \input{top_perfomances.tex}
    }
\end{center}
\caption{Top performances for each tournament type based on $\bar{r}$.}
\label{table:top_performances}
\end{table}

In standard tournaments 10 out of the 15 top strategies are introduced
in~\cite{Harper2017}. These are strategies based on finite state automata (FSM),
hidden markov models (HMM), artificial neural networks (ANN), lookup tables
(LookerUp) and stochastic lookup tables (Gambler) that have been trained using
reinforcement learning algorithms (evolutionary and particle swarm algorithms).
They have been trained to perform well against the strategies
in APL in a standard tournament, thus their performance in the
specific setting was anticipated. DoubleCrosser, and Fool Me Once, are
strategies not from the literature but from the APL. DoubleCrosser
is a strategy that makes use of the number of turns because it is set to defect on
the last two rounds. The strategy was expected to not perform as well in
tournaments where the number of turns is not specified, but the strategy did not
perform well in tournaments with noise either. Finally, Winner
12~\cite{mathieu2017} and DBS~\cite{Au2006} are both from the the literature.
DBS is strategy specifically designed for noisy environments, however, it ranks
highly only in standard ones.

@@

\begin{table}[!htbp]
    \centering
    \resizebox{.30\textwidth}{!}{
    \input{performance_noise_subset_table.tex}}
    \caption{Top performances in 5661 noisy tournaments where \(p_n<0.5\).}\label{table:subset_noise_result}
\end{table}

@@

\begin{table}[!htbp]
    \centering
    \resizebox{.30\textwidth}{!}{
    \input{performance_probend_subset_table.tex}}
    \caption{Top performances in 1139 probabilistic ending tournaments with \(p_e < 0.1\)}
    \label{table:subset_probend_result}
\end{table}

@@

@@

\section{Acknowledgements}

A variety of software have been used in this work:

\begin{itemize}
    \item The Axelrod-Python library for IPD simulations~\cite{axelrodproject}.
    \item The Matplotlib library for visualisation~\cite{hunter2007matplotlib}.
    \item The Numpy library for data manipulation~\cite{walt2011numpy}.
    \item The scikit-learn library for data analysis~\cite{scikit-learn}.
\end{itemize}

\appendix

\section{A summary of parameters}\label{app:parameters}

\begin{table}[h]
    \begin{center}
    \resizebox{.7\textwidth}{!}{
    \begin{tabular}{llc}
    \toprule
feature & feature explanation \\
 \midrule
stochastic                  & If a strategy is stochastic \\
makes use of game           & If a strategy makes used of the game information  \\
makes use of length         & If a strategy makes used of the number of turns \\
memory usage                & The memory size of a strategy divided by the number of turns \\
SSE                         & A measure of how far a strategy is from extortionate behaviour \\
$C_{\text{max}}$          & The biggest cooperating rate in the tournament \\
$C_{\text{min}}$          & The smallest cooperating rate in the tournament \\
$C_{\text{median}}$       & The median cooperating rate in the tournament \\
$C_{\text{mean}}$         & The mean cooperating rate in the tournament \\
$C_r$ / $C_{\text{max}}$    & A strategy's cooperating rate divided by the maximum \\
$C_r$ / $C_{\text{min}}$    & A strategy's cooperating rate divided by the minimum \\
$C_r$ / $C_{\text{median}}$ & A strategy's cooperating rate divided by the median \\
$C_r$ / $C_{\text{mean}}$   & A strategy's cooperating rate divided by the mean \\
$C_r$                       & The cooperating ratio of a strategy \\
$CC$ to $C$ rate            & The probability a strategy will cooperate after a mutual cooperation \\
$CD$ to $C$ rate            & The probability a strategy will cooperate after being betrayed by the opponent \\
$DC$ to $C$ rate            & The probability a strategy will cooperate after betraying the opponent\\
$DD$ to $C$ rate            & The probability a strategy will cooperate after a mutual defection\\
$p_n$                       & The probability of a player's action being flipped at each interaction \\
$n$                         & The number of turns \\
$p_e$                       & The probability of a match ending in the next turn \\
$N$                         & The number of strategies in the tournament \\
$k$                         & The number that a given tournament is repeated \\
    \bottomrule
        \end{tabular}}
    \end{center}
    \caption{The features which are included in the performance evaluation analysis.}\label{table:parameters_summary}
\end{table}

\section{List of strategies}\label{app:list_of_players}

The strategies used in this study which are from Axelrod-Python library version 3.0.0.

\begin{multicols}{3}
	\begin{enumerate}
		\input{list_of_strategies.tex}
	\end{enumerate}
\end{multicols}

\section{Correlation coefficients}\label{app:correlations}

A graphical representation of the correlation coefficients for the features in
Table~\ref{table:manual_features}.

\begin{figure}[!htbp]
        \begin{center}
            \includegraphics[width=.75\linewidth]{../images/standard_correlation_plot.pdf}
        \end{center}
        \caption{Correlation coefficients of features in Table~\ref{table:manual_features}
        for standard tournaments}
\end{figure}
\begin{figure}[!htbp]
    \begin{center}
        \includegraphics[width=.75\linewidth]{../images/noise_correlation_plot.pdf}
    \end{center}
    \caption{Correlation coefficients of features in Table~\ref{table:manual_features}
    for noisy tournaments}
\end{figure}
\begin{figure}[!htbp]
    \begin{center}
        \includegraphics[width=.75\linewidth]{../images/probend_correlation_plot.pdf}
    \end{center}
    \caption{Correlation coefficients of features in Table~\ref{table:manual_features}
    for probabilistic ending tournaments}
\end{figure}
\begin{figure}[!htbp]
    \begin{center}
        \includegraphics[width=.75\linewidth]{../images/probend_noise_correlation_plot.pdf}
    \end{center}
    \caption{Correlation coefficients of features in Table~\ref{table:manual_features}
    for noisy probabilistic ending tournaments}
\end{figure}
\begin{figure}[!htbp]
    \begin{center}
        \includegraphics[width=.75\linewidth]{../images/merged_correlation_plot.pdf}
    \end{center}
    \caption{Correlation coefficients of features in Table~\ref{table:manual_features}
    for data set}
\end{figure}

>>>>

The top 15 strategies for each tournament type based on \(\bar{r}\) are given in
Table~\ref{table:top_performances}. Table~\ref{table:top_performances} includes
the top 15 strategies in noisy tournaments with \(p_n < 0.1\) and probabilistic
ending tournaments with \(p_e < 0.1\). These are included because the most common
values in the literature for the probabilities of noise and a match ending are
less than 0.1.

\newcolumntype{g}{>{\columncolor{Gray}}l}
\begin{table}[!htbp]
    \begin{center}
    \resizebox{\textwidth}{!}{
        \input{top_perfomances.tex}
    }
\end{center}
\caption{Top performances for each tournament type based on $\bar{r}$.}
\label{table:top_performances}
\end{table}

In standard tournaments 10 out of the 15 top strategies are introduced
in~\cite{Harper2017}. These are strategies based on finite state automata (FSM),
hidden markov models (HMM), artificial neural networks (ANN), lookup tables
(LookerUp) and stochastic lookup tables (Gambler) that have been trained using
reinforcement learning algorithms (evolutionary and particle swarm algorithms).
They have been trained to perform well against the strategies
in APL in a standard tournament, thus their performance in the
specific setting was anticipated. DoubleCrosser, and Fool Me Once, are
strategies not from the literature but from the APL. DoubleCrosser
is a strategy that makes use of the number of turns because it is set to defect on
the last two rounds. The strategy was expected to not perform as well in
tournaments where the number of turns is not specified, but the strategy did not
perform well in tournaments with noise either. Finally, Winner
12~\cite{mathieu2017} and DBS~\cite{Au2006} are both from the the literature.
DBS is strategy specifically designed for noisy environments, however, it ranks
highly in standard tournaments as well.

@@

% \begin{table}[!htbp]
%     \centering
%     \resizebox{.30\textwidth}{!}{
%     \input{performance_noise_subset_table.tex}}
%     \caption{Top performances in 5661 noisy tournaments where \(p_n<0.5\).}\label{table:subset_noise_result}
% \end{table}

@@

% \begin{table}[!htbp]
%     \centering
%     \resizebox{.30\textwidth}{!}{
%     \input{performance_probend_subset_table.tex}}
%     \caption{Top performances in 1139 probabilistic ending tournaments with \(p_e < 0.1\)}
%     \label{table:subset_probend_result}
% \end{table}

@@

\newcolumntype{g}{>{\columncolor{Gray}}c}
\begin{table}[h]
    \begin{center}
\resizebox{.8\textwidth}{!}{
    \input{regression_table.tex}}
    \end{center}
\end{table}

@@

% \section{Acknowledgements}

% A variety of software have been used in this work:

% \begin{itemize}
%     \item The Axelrod-Python library for IPD simulations~\cite{axelrodproject}.
%     \item The Matplotlib library for visualisation~\cite{hunter2007matplotlib}.
%     \item The Numpy library for data manipulation~\cite{walt2011numpy}.
%     \item The scikit-learn library for data analysis~\cite{scikit-learn}.
% \end{itemize}

% \appendix

% \section{A summary of parameters}\label{app:parameters}

% \begin{table}[h]
%     \begin{center}
%     \resizebox{.7\textwidth}{!}{
%     \begin{tabular}{llc}
%     \toprule
% feature & feature explanation \\
%  \midrule
% stochastic                  & If a strategy is stochastic \\
% makes use of game           & If a strategy makes used of the game information  \\
% makes use of length         & If a strategy makes used of the number of turns \\
% memory usage                & The memory size of a strategy divided by the number of turns \\
% SSE                         & A measure of how far a strategy is from extortionate behaviour \\
% $C_{\text{max}}$          & The biggest cooperating rate in the tournament \\
% $C_{\text{min}}$          & The smallest cooperating rate in the tournament \\
% $C_{\text{median}}$       & The median cooperating rate in the tournament \\
% $C_{\text{mean}}$         & The mean cooperating rate in the tournament \\
% $C_r$ / $C_{\text{max}}$    & A strategy's cooperating rate divided by the maximum \\
% $C_r$ / $C_{\text{min}}$    & A strategy's cooperating rate divided by the minimum \\
% $C_r$ / $C_{\text{median}}$ & A strategy's cooperating rate divided by the median \\
% $C_r$ / $C_{\text{mean}}$   & A strategy's cooperating rate divided by the mean \\
% $C_r$                       & The cooperating ratio of a strategy \\
% $CC$ to $C$ rate            & The probability a strategy will cooperate after a mutual cooperation \\
% $CD$ to $C$ rate            & The probability a strategy will cooperate after being betrayed by the opponent \\
% $DC$ to $C$ rate            & The probability a strategy will cooperate after betraying the opponent\\
% $DD$ to $C$ rate            & The probability a strategy will cooperate after a mutual defection\\
% $p_n$                       & The probability of a player's action being flipped at each interaction \\
% $n$                         & The number of turns \\
% $p_e$                       & The probability of a match ending in the next turn \\
% $N$                         & The number of strategies in the tournament \\
% $k$                         & The number that a given tournament is repeated \\
%     \bottomrule
%         \end{tabular}}
%     \end{center}
%     \caption{The features which are included in the performance evaluation analysis.}\label{table:parameters_summary}
% \end{table}

% \section{List of strategies}\label{app:list_of_players}

% The strategies used in this study which are from Axelrod-Python library version 3.0.0.

% \begin{multicols}{3}
% 	\begin{enumerate}
% 		\input{list_of_strategies.tex}
% 	\end{enumerate}
% \end{multicols}

% \section{Correlation coefficients}\label{app:correlations}

% A graphical representation of the correlation coefficients for the features in
% Table~\ref{table:manual_features}.

% \begin{figure}[!htbp]
%         \begin{center}
%             \includegraphics[width=.75\linewidth]{../images/standard_correlation_plot.pdf}
%         \end{center}
%         \caption{Correlation coefficients of features in Table~\ref{table:manual_features}
%         for standard tournaments}
% \end{figure}
% \begin{figure}[!htbp]
%     \begin{center}
%         \includegraphics[width=.75\linewidth]{../images/noise_correlation_plot.pdf}
%     \end{center}
%     \caption{Correlation coefficients of features in Table~\ref{table:manual_features}
%     for noisy tournaments}
% \end{figure}
% \begin{figure}[!htbp]
%     \begin{center}
%         \includegraphics[width=.75\linewidth]{../images/probend_correlation_plot.pdf}
%     \end{center}
%     \caption{Correlation coefficients of features in Table~\ref{table:manual_features}
%     for probabilistic ending tournaments}
% \end{figure}
% \begin{figure}[!htbp]
%     \begin{center}
%         \includegraphics[width=.75\linewidth]{../images/probend_noise_correlation_plot.pdf}
%     \end{center}
%     \caption{Correlation coefficients of features in Table~\ref{table:manual_features}
%     for noisy probabilistic ending tournaments}
% \end{figure}
% \begin{figure}[!htbp]
%     \begin{center}
%         \includegraphics[width=.75\linewidth]{../images/merged_correlation_plot.pdf}
%     \end{center}
%     \caption{Correlation coefficients of features in Table~\ref{table:manual_features}
%     for data set}
% \end{figure}
